A comparison of single-cell trajectory inference methods: towards more accurate and robust tools

### 2018-04-03 analysis/paper/paper.Rmd
whatever

# Supplementary Material

@@

```{r "supplementary", echo=FALSE, results='asis'}
source(paste0(dynalysis::get_dynalysis_folder(), "/analysis/paper/sfigs_stables.R"))
```

>>>>

## Data and code availability
The datasets used in this study are deposited in zenodo [doi.org/10.5281/zenodo.1211533](doi.org/10.5281/zenodo.1211533). Code is available as several R packages on github [https://github.com/dynverse/dynverse](https://github.com/dynverse/dynverse).

@@

```{r "supplementary", echo=FALSE, results='asis'}
if (params$table_format == "html") 
  source(paste0(dynalysis::get_dynalysis_folder(), "/analysis/paper/sfigs_stables.R"))
write_rds(lst(sfigs, stables), derived_file("sfigs_stables.rds", "paper"))
```
